---
output:
  word_document: default
  pdf_document: default
  html_document: default
---

##MARS


###General
#importing and installing all the necessary packages
```{r, echo = TRUE}
install.packages("dplyr")
install.packages("ggplot2")
install.packages("earth")
install.packages("caret")
library(dplyr)
library(ggplot2)
library(earth)
library(caret)
```

###Data
#loading up the data and reading the csv file
```{r, echo = TRUE}
setwd("C:\\Users\\anast\\Documents\\R")
data <-read.csv(file="sensitivityanalysis2.csv",head=TRUE,sep=",")
data
```

###MARS
```{r, echo = TRUE}
library(dplyr)
library(ggplot2)
library(earth)
library(caret)
datax=data[c(1:811),c(1:3)];
mars1 <-earth(data$GlycerolMoleFraction ~ ., data = datax,degree=3)
print(mars1)
summary(mars1)
plot(mars1)

#uses a grid to characterize all the data inputs
prediction <- predict(mars1,datax)
prediction
hyper_grid <- expand.grid(
  degree = 1:3, 
  nprune = seq(2, 100, length.out = 10) %>% floor()
)
head(hyper_grid)
set.seed(123)  # for reproducibility
#trains the MARS model to create regressions using a grid search
cv_mars <- train(
  x = subset(datax),
  y = data$GlycerolMoleFraction,
  method = "earth",
  metric = "RMSE",
  trControl = trainControl(method = "cv", number = 10),
  tuneGrid = hyper_grid
)
#finds the best results from predictions and gets the model summary
cv_mars$bestTune
cv_mars$results %>%
  filter(nprune == cv_mars$bestTune$nprune, degree == cv_mars$bestTune$degree)
ggplot(cv_mars)
summary(cv_mars)
prediction <- predict(cv_mars,datax)
prediction
```

###Plotting the subset regressions 

###Views how the total molar flow and glycerol mole frac affect each other
```{r}
cv_mars$resample
library(pdp)
library(vip)
p1 <- partial(cv_mars, pred.var = "TotalMolarFlow", grid.resolution = 20)

  plot(p1, type ="l", xlab = "TotalMolarFlow", ylab = "GlycerolMoleFrac", lwd = 2, 
  main = "GlycerolMoleFrac vs TotalMolarFlow")

```
###Views how the FeedTemperature and GlycerolMoleFrac affect each other
```{r}
p2 <- partial(cv_mars, pred.var = "FeedTemperature", grid.resolution = 20)

  plot(p2, type ="l", xlab = "FeedTemperature", ylab = "GlycerolMoleFrac", lwd = 2, 
  main = "GlycerolMoleFrac vs TotalMolarFlow")


```
###Views how the ColumnRefluxRatio and GlycerolMoleFrac affect each other
```{r}
p3 <- partial(cv_mars, pred.var = "ColumnRefluxRatio", grid.resolution = 20)

  plot(p3, type ="l", xlab = "ColumnRefluxRatio", ylab = "GlycerolMoleFrac", lwd = 2, 
  main = "GlycerolMoleFrac vs TotalMolarFlow")


```

###Making the 3D plot for all three variable
```{r}
p4 <- partial(cv_mars, pred.var = c("TotalMolarFlow", "ColumnRefluxRatio"), 
              grid.resolution = 10) %>% 
  plotPartial(levelplot = FALSE, zlab = "GlycerolMoleFrac", drape = TRUE, colorkey = TRUE, 
              screen = list(z = -20, x = -60))

  plot(p4)

```